FitBit Analysis

### 2023-02-16 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
fitbit bla

---
title: "Fitbit & ET Glasses - Methods"
output: html_notebook
---
```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Packages
# install.packages("needs")
# Choose "No"
library(needs)
needs(tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr)
```

@@

# disruption & confidence rating
df_rating <- 
  excel_sheets("data/Coding_SRI.xlsx") %>% 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
  select(ID, # select relevant columns 
         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
         confidence_factor,
         event
         ) %>% 
  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                    yes = NA,
                                    no = disruption_factor
                                    ),
         confidence_factor = ifelse(confidence_factor < 0,
                                   yes = NA,
                                   no = confidence_factor),
         event = as_factor(event)
         ) %>% 
  na.omit() 
  # group_by(ID) %>% 
  # summarise("mean_disrup" = round(mean(disruption_factor), 2),
  #           "mean_confi" = round(mean(confidence_factor), 2))

@@

main <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) %>% 
  mutate(time = .$Time - min(.$Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "after",
                               str_detect(string = id, pattern = "_m") ~ "main",
                               str_detect(string = id, pattern = "_p") ~ "pre",
                               str_detect(string = id, pattern = "_s") ~ "subsequent",
                               str_detect(string = id, pattern = "_i") ~ "interview",
                               TRUE ~ "overall"
                               ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) %>%
      # filter(time <= 600) %>% # filter for 10min intervals
    filter(time <= 9000) %>% # filter for 2 hours 30min (maximal duration of study)
    select(!c("Time","Heart Rate","id"))
    ) %>%
  bind_rows()

@@

df_anova <-
  main %>% 
  filter(time_span != "overall") %>%   
  select("ID",
         "time_span",
         "heart_rate",
         "teaching_experience",
         "disruption_factor",
         "confidence_factor") %>% 
  mutate(time_span = fct_recode(time_span,
                                "Pre-Lehrphase" = "pre",
                                "Lehrphase" = "main",
                                "Post-Lehrphase" = "subsequent",
                                "Interviewphase" = "interview",
                                "Endphase" = "after"
                                ),
         time_span = factor(time_span,
                            levels = c("Pre-Lehrphase",
                                       "Lehrphase",
                                       "Post-Lehrphase",
                                       "Interviewphase",
                                       "Endphase"
                                       )
                            )
         ) %>%
  distinct() %>% 
  group_by(ID, time_span) %>%
  summarise(mean_hr = mean(heart_rate, na.rm = TRUE),
            mean_confi = mean(disruption_factor, na.rm = TRUE),
            mean_disrup = mean(disruption_factor, na.rm = TRUE),
            mean_te = mean(teaching_experience, na.rm = TRUE)
         )

@@

# effect size of ANOVA
install.packages("DescTools")
library(DescTools)
EtaSq(df_anova_phase)

effect_size_anova <-
  sqrt(0.3399757/(1-0.3399757))

# effect size of pairwise comparisons
library(dplyr)
library(rstatix)
df_anova_subset %>%
cohens_d(mean_hr~time_span) %>% 
as.data.frame()

@@

>>>>

---
title: "Fitbit & ET Glasses - Methods"
output: html_notebook
---
```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Packages
# install.packages("needs")
# Choose "No"
library(needs)
needs(tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      psych)

@@

# read in data
# disruption & confidence rating
df_rating <- 
  excel_sheets("data/Coding_SRI.xlsx") %>% 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
  dplyr::select(ID, # select relevant columns 
         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
         confidence_factor,
         event
         ) %>% 
  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                    yes = NA,
                                    no = disruption_factor
                                    ),
         confidence_factor = ifelse(confidence_factor < 0,
                                   yes = NA,
                                   no = confidence_factor),
         event = as_factor(event)
         ) %>% 
  na.omit() 
  # group_by(ID) %>% 
  # summarise("mean_disrup" = round(mean(disruption_factor), 2),
  #           "mean_confi" = round(mean(confidence_factor), 2))

@@

main <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) %>% 
  mutate(time = .$Time - min(.$Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "after",
                               str_detect(string = id, pattern = "_m") ~ "main",
                               str_detect(string = id, pattern = "_p") ~ "pre",
                               str_detect(string = id, pattern = "_s") ~ "subsequent",
                               str_detect(string = id, pattern = "_i") ~ "interview",
                               TRUE ~ "overall"
                               ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) %>%
      # filter(time <= 600) %>% # filter for 10min intervals
    filter(time <= 9000) %>% # filter for 2 hours 30min (maximal duration of study)
    dplyr::select(!c("Time","Heart Rate","id"))
    ) %>%
  bind_rows()

@@

# data wrangling - preparing data for anova
df_anova <-
  main %>% 
  filter(time_span != "overall") %>%   
  dplyr::select("ID",
         "time_span",
         "heart_rate",
         "teaching_experience",
         "disruption_factor",
         "confidence_factor") %>% 
  mutate(time_span = fct_recode(time_span,
                                "Pre-Lehrphase" = "pre",
                                "Lehrphase" = "main",
                                "Post-Lehrphase" = "subsequent",
                                "Interviewphase" = "interview",
                                "Endphase" = "after"
                                ),
         time_span = factor(time_span,
                            levels = c("Pre-Lehrphase",
                                       "Lehrphase",
                                       "Post-Lehrphase",
                                       "Interviewphase",
                                       "Endphase"
                                       )
                            )
         ) %>%
  distinct() %>% 
  group_by(ID, time_span) %>%
  summarise(mean_hr = mean(heart_rate, na.rm = TRUE),
            mean_confi = mean(confidence_factor, na.rm = TRUE),
            mean_disrup = mean(disruption_factor, na.rm = TRUE),
            mean_te = mean(teaching_experience, na.rm = TRUE)
         )

# counting participants in individual phases
table(df_anova['time_span'])

# descriptive analysis
describeBy(df_anova$mean_hr,
           df_anova$time_span)

@@

# effect size of ANOVA
EtaSq(df_anova_phase)

effect_size_anova <-
  sqrt(0.3413791   /(1-0.3413791   ))

# effect size of pairwise comparisons
library(dplyr)
library(rstatix)
effect_size_pwc <-
  df_anova_subset %>%
  cohens_d(mean_hr~time_span) %>% 
  as.data.frame()

@@

### Multiple Regression

# AV = mittlere Herzrate in teaching phase; UV1 = Störfaktor, UV2 = Sicherheitsfaktor, UV3= Lehrerfahrung

df_lm_subset <- df_anova %>% 
  filter(time_span == "Lehrphase") %>% 
  dplyr::select(mean_hr, 
               mean_disrup, 
               mean_confi,
               mean_te)

modell <-   lm(mean_hr ~ mean_confi + mean_disrup + mean_te, 
               data = df_lm_subset,
               family = binomial)
summary(modell)

cor(df_lm_subset)

### 2023-02-16 02_paper/02_study/02_fitbit paper/Presentation_Analysis.Rmd
fitbit bla

# disruption & confidence rating
df_rating <- 
  excel_sheets("data/Coding_SRI.xlsx") %>% 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
  select(ID, # select relevant columns 
         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
         confidence_factor,
         event
         ) %>% 
  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                    yes = NA,
                                    no = disruption_factor
                                    ),
         confidence_factor = ifelse(confidence_factor < 0,
                                   yes = NA,
                                   no = confidence_factor),
         event = as_factor(event)
         )

@@

  main %>% 
  filter(time_span == "overall") %>% 
  select("ID","time_span", "time","heart_rate") %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_smooth() +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Zeit (in Sekunden)",
       y = "Herzrate (in Schlägen pro Minute)") +
  theme_apa()

>>>>

# disruption & confidence rating
df_rating <- 
  excel_sheets("data/Coding_SRI.xlsx") %>% 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
  dplyr::select(ID, # select relevant columns 
         disruption_factor, # -99 = subject did not notice event; -100 = experimenter did not asked for event
         confidence_factor,
         event
         ) %>% 
  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                    yes = NA,
                                    no = disruption_factor
                                    ),
         confidence_factor = ifelse(confidence_factor < 0,
                                   yes = NA,
                                   no = confidence_factor),
         event = as_factor(event)
         )

@@

  main %>% 
  filter(time_span == "overall") %>% 
  dplyr::select("ID","time_span", "time","heart_rate") %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_smooth() +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Zeit (in Sekunden)",
       y = "Herzrate (in Schlägen pro Minute)") +
    theme_apa()

############## neuer Plot für GEBF #################

  plot_overall <-
  main %>% 
  filter(time_span == "overall") %>%
  dplyr::select("ID","time_span", "time","heart_rate") %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_smooth() +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  labs(x = "Zeit (in Sekunden)",
       y = "Herzrate (in Schlägen pro Minute)") +
  ggtitle("Gesamtverlauf der Herzrate in unterschiedlichen Phasen") +
  theme(text = element_text(family = "serif"),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20),
        strip.text = element_text(size = 16),
        plot.title = element_text(size = 20, 
                                  face = "bold")) + 
    theme_apa() 
    # facet_grid(cols = vars(time_span),
    #          scales = "free_x")

### 2023-02-16 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
update fitbit
fitbit bla

main <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) %>% 
  mutate(time = .$Time - min(.$Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "after",
           str_detect(string = id, pattern = "_m") ~ "main",
           str_detect(string = id, pattern = "_p") ~ "pre",
           str_detect(string = id, pattern = "_s") ~ "subsequent",
           str_detect(string = id, pattern = "_i") ~ "interview",
           TRUE ~ "overall"
           ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) %>%
      filter(time <= 600) %>%
    select(!c("Time","Heart Rate","id"))
    ) %>%
  bind_rows()

# main <-
#   left_join(main, df_merge,
#             by = "ID")

>>>>

main <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) %>% 
  mutate(time = .$Time - min(.$Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "after",
           str_detect(string = id, pattern = "_m") ~ "main",
           str_detect(string = id, pattern = "_p") ~ "pre",
           str_detect(string = id, pattern = "_s") ~ "subsequent",
           str_detect(string = id, pattern = "_i") ~ "interview",
           TRUE ~ "overall"
           ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) %>%
      filter(time <= 600) %>%
     dplyr::select(!c("Time","Heart Rate","id"))
    ) %>%
  bind_rows()

main <-
  left_join(main, df_merge,
            by = "ID")
